EDIpack 2.0: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-21 05_examples.tex
Adding W2Dyn comparision, included figure.
GB wide pass on many parts of the text

@@

The evolution of this order parameter is presented in panel (B), 
highlighting the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ shows the 
characteristic exponential growth with $U$, reflecting the formation 
of weakly bound Cooper pairs. This regime is known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$, 
indicating tightly bound local pairs. Comparison with the mean-field result 
(gray line) reveals the effect of local quantum fluctuations, which 
slightly suppress the order parameter, particularly in the intermediate 
regime.

To quantify these correlation effects, we plot in panel (C) the 
\emph{correlation strength}
$\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
where $S(i\omega)$ is the anomalous self-energy.
This ratio statically captures 
the maximum amplitude of its dynamical dependence by comparing the high-energy 
mean-field-like limit with the low-energy behavior at the Fermi level. 
Large values of $\Theta$ indicate a strongly correlated state with 
significant dynamical effects, hence a more correlated state.
Our results show that both the weak 
and strong coupling limits are relatively close to the mean-field 
description, while the intermediate regime is marked by strong 
correlations, significantly departing from the BCS picture.

To further illustrate the impact of dynamical correlations, we 
present in panel (D) the evolution of the double occupancy 
$d = \langle n_\up n_\dw \rangle$ as a function of $U$. At half-filling, 
the mean-field expression for this quantity is $d = 1/4 + \phi^2$, 
reflecting the sole contribution of the order parameter. Our DMFT 
results show a slight increase in $d$ over the mean-field prediction 
in the weak coupling regime, indicating enhanced local correlations. 
However, as $U$ increases, the double occupancy quickly drops below 
the mean-field result, reflecting the onset of strong pairing and 
pair localization in the BEC limit.

>>>>

\begin{figure}%[t!]
  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
    \caption{\label{figEx1W}%
        }
\end{figure}

@@

The evolution of this order parameter is presented in panel (B), 
highlighting the crossover from the weak-coupling BCS regime to the 
strong-coupling BEC regime. In the BCS limit, $\phi$ shows the 
characteristic exponential growth with $U$, reflecting the formation 
of weakly bound Cooper pairs. This regime is known to be 
computationally challenging. In the opposite, strong-coupling, limit 
$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$, 
indicating tightly bound local pairs. Comparison with the mean-field result 
(gray line) reveals the effect of local dynamical fluctuations, which 
slightly suppress the order parameter, particularly in the intermediate 
regime.

To quantify these dynamical effects, we plot in panel (C) the 
\emph{correlation strength}
$\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
where $S(i\omega)$ is the anomalous self-energy.
This ratio encapsulates, in a single positive number, % sorry, but "statically captures" sounded quite mysterious to me (I guess it refers to having just a single number, but it requires hard mental processing, imho)
the amplitude of the dynamical dependence of $S(i\omega)$ by comparing its 
BCS-like limit at high energy with the low-energy behavior at the Fermi level. 
Large values of $\Theta$ indicate an anomalous self-energy with 
significant dynamical effects, hence a more correlated superconducting state.
Our results show that both the weak 
and strong coupling limits are relatively close to the BCS results, 
while the intermediate regime is marked by strong 
correlations, significantly departing from the mean-field picture.

To further illustrate the impact of dynamical fluctuations, we 
present in panel (D) the evolution of the double occupancy 
$d = \langle n_\up n_\dw \rangle$ as a function of $U$. At half-filling, 
the mean-field expression for this quantity is $d = 1/4 + \phi^2$, 
reflecting the sole contribution of the order parameter. Our DMFT 
results show a slight increase in $d$ over the mean-field prediction 
in the weak coupling regime, corresponding to a steep growth of
the correlation strength $\Theta$. 
However, as $U$ increases, the double occupancy drops below 
the BCS result, reflecting the onset of strong pairing and 
pair localization in the BEC limit. Correspondingly, $\Theta$ 
progressively decreases at large $U$ attraction strength.
